Morse Theory

### 2020-12-05 paper.tex
Adding Introductionw

\tableofcontents
\newpage
\section{Morse Theory}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% % begin N1
\subsection{Introduction}

>>>>

\tableofcontents
\newpage
A smooth function is always good to have. However, some critical points might have equal function values. Morse functions are such ones that don't have the latter property. 
Sometimes we would like to analyze a function, using its level sets. A Reeb graph helps us plot the evolution of the components of a level set. Morse functions and Reeb graphs are extremely useful
in some contexts. They have applications in topological data analysis, computer graphics, and even in oceanography.
\section{Morse Theory}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% % begin N1
\subsection{Introduction}
